Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2011-11-03 Multiresolution_framework/ltx/manuscript.tex
minor edits

For the linear state-space model given by (\ref{eq:StateEquation}--\ref{eq:MRA-Observationmatrix}), the joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ can be written as

@@

&-T_s^2\varsigma^2\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t-2\xi \varsigma T_s\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t\nonumber \\

@@

\beta=-\ln \mid \boldsymbol\Sigma_w\mid-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\xi\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t

@@

The three traces that form \eqref{eq:MRA-QintermsofTraces} are dealt with in turn. To begin, the first trace is written in terms of element-wise summations

@@

$\boldsymbol\Lambda_{\theta}$&\eqref{eq:MRA-Lambdatheta}&$O(n_x^2n_{\theta})$&-\\

>>>>

For the linear state-space model given by (\ref{eq:StateEquation}--\ref{eq:Observationmatrix}), the joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$ can be written as

@@

&-T_s^2\varsigma^2\mathbf x_t^\top \boldsymbol\Lambda_{\theta}^\top\boldsymbol\Lambda_x^{-1}\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t-2\xi \varsigma T_s\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\boldsymbol\Lambda_x^{-1}\boldsymbol\Lambda_{\theta}\mathbf x_t,\nonumber \\

@@

\beta=-\ln \mid \boldsymbol\Sigma_w\mid-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}+2\xi\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t-\xi^2\mathbf x_t^\top\boldsymbol\Sigma_w^{-1}\mathbf x_t,

@@

Note that the expectation distributes over the trace sum. The three traces that form \eqref{eq:MRA-QintermsofTraces} are dealt with in turn. To begin, the first trace is written in terms of element-wise summations

@@

$\boldsymbol\Lambda_{\theta}$&\eqref{eq:Lambdatheta}&$O(n_x^2n_{\theta})$&-\\
